Topological Equivariant Artist Model

### 2021-12-31 slides/main.tex
artist nt + category sheaves
page #s

\documentclass[xcolor={dvipsnames}, handout]{beamer}
%\documentclass[xcolor={dvipsnames}]{beamer}
%\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{amsmath, amsfonts, amssymb, mathtools, eulervm, xspace}
\renewcommand{\restriction}{\mathord{\upharpoonright}} %restriction w/p space
\usepackage{bm}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?

@@

\begin{frame}{Fiber Bundles}
    \begin{columns}
        \column{0.39\textwidth}
            \begin{equation*}
                %\label{eq:related-work:continuity:fiber-bundle}
                \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
                  \onslide*<2-|handout:2->{\dfiberc} \onslide*<4-|handout:4->{\arrow[r, hook]} \& \onslide*<3|handout:3->{\dtotalc} \onslide*<4-|handout:4->{\arrow[d, "\pi"']} \\
                   \& \onslide*<1-|handout:1->{\dbasec} \onslide*<5-|handout:5->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
                \end{tikzcd}
            \end{equation*}
     \column{0.59\textwidth}
        \begin{description}
            \item<1-|handout:1->[\textcolor{base}{Base Space}] $( \dbasec, \mathcal{T})$, $\dbasepointc \in \opensetc \subset \dbasec$
            \item<2-|handout:2->[\textcolor{fiber}{Fiber Space}] $\dfiberc_{\dbasepointc} = \pi^{-1}(\dbasepointc)$
            \item<3-|handout:3->[\textcolor{total}{Total Space}]  $\dtotalc\restriction_{\opensetc} = \dbasec\restriction_{\opensetc} \times \dfiberc\restriction_{\opensetc}$ \\ for all $\opensetc \subset K$ 
        \end{description}
    \end{columns}
    \pause
    \begin{alertblock}<5-|handout:5->{Sections}
    $\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\openset} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}$
    \end{alertblock}
\end{frame}

@@

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<8-|handout:8->{\dfiberc}
        \onslide*<8-|handout:8->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:3->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3-|handout:3->{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} \& 
            {} \& 
            \onslide*<5-|handout:5->{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<6-|handout:6->{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<2|handout:2>{\opensetc_1 \subset \dbasec}
            \onslide*<3-|handout:3->{\opensetc_1} 
            \onslide*<4-|handout:4->{\arrow[uu, "\sheafc_{\dbasec}", color=sheaf]} 
            \onslide*<6-|handout:6->{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<7-|handout:7->{\arrow[uu, "\sheafc_{\dbasec}" description, dotted, color=sheaf]} \& 
            \onslide*<5-|handout:5->{\opensetc_2} 
            \onslide*<5-|handout:5->{\arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{description}
        \item<8-|handout:8->[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<9-|handout:9>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}

@@

\begin{frame}{$\vartist_{\vindexpullc}: \vindexpullc\sheafc_{\dbasec} \rightarrow \sheafc_{\gbasec}$}

\end{frame}
\begin{comment}

>>>>

\documentclass[xcolor={dvipsnames}, handout]{beamer}
%\documentclass[xcolor={dvipsnames}]{beamer}
\setbeamertemplate{footline}[frame number]
%\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{amsmath, amsfonts, amssymb, mathtools, eulervm, xspace}
\renewcommand{\restriction}{\mathord{\upharpoonright}} %restriction w/p space
\usepackage{bm}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?

@@

\begin{frame}{Fiber Bundles}
    \begin{columns}
        \column{0.39\textwidth}
            \begin{equation*}
                %\label{eq:related-work:continuity:fiber-bundle}
                \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
                  \onslide*<2-|handout:1>{\dfiberc} 
                  \onslide*<4-|handout:1>{\arrow[r, hook]} \& 
                  \onslide*<3|handout:1>{\dtotalc} 
                  \onslide*<4-|handout:1>{\arrow[d, "\pi"']} \\
                   \& \onslide*<1-|handout:1>{\dbasec} 
                   \onslide*<5-|handout:1>{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
                \end{tikzcd}
            \end{equation*}
     \column{0.59\textwidth}
        \begin{description}
            \item<1-|handout:1>[\textcolor{base}{Base Space}] $( \dbasec, \mathcal{T})$, $\dbasepointc \in \opensetc \subset \dbasec$
            \item<2-|handout:1>[\textcolor{fiber}{Fiber Space}] $\dfiberc_{\dbasepointc} = \pi^{-1}(\dbasepointc)$
            \item<3-|handout:1>[\textcolor{total}{Total Space}]  $\dtotalc\restriction_{\opensetc} = \dbasec\restriction_{\opensetc} \times \dfiberc\restriction_{\opensetc}$ \\ for all $\opensetc \subset K$ 
        \end{description}
    \end{columns}
    \pause
    \begin{alertblock}<5-|handout:1>{Sections}
    $\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\openset} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}$
    \end{alertblock}
\end{frame}

@@

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:9->{\dfiberc}
        \onslide*<9-|handout:9->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:3->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:3,6->{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:4-5>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc} 
            \&  
            {} \& 
            \onslide*<6-|handout:6->{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:7->{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:3>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:4-5>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:6->{\opensetc_1} 
            \onslide*<5-|handout:5->{\arrow[uu, "\sheafc_{\dbasec}", color=sheaf]} 
            \onslide*<7-|handout:7->{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:8->{\arrow[uu, "\sheafc_{\dbasec}" description, color=sheaf]} \& 
            \onslide*<6-|handout:6->{\opensetc_2} 
            \onslide*<6-|handout:6->{\arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{description}
        \item<8-|handout:9->[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<9-|handout:10>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}

@@

\begin{frame}{$\vartist_{\vindexpushc}: \sheafc_{\dbasec} \rightarrow \vindexpushc\sheafc_{\gbasec}$}
    \begin{equation}
      \begin{tikzcd}[ampersand replacement =\&]
        \cgamma{\opensetc_1}{\dtotalc} 
        \arrow[dd, "\iota^*"', hook, color=set] 
        \arrow[rrrr, "\vartistc_{\opensetc_1}", bend left, color=artist] \&  \& 
        \opensetc_1 
        \arrow[ll, "\sheafc_{\dtotalc}", color=sheaf] 
        \arrow[rr, "\sheafc_{\gtotalpushc}"', color=sheaf] \&  \& 
        \cgamma{\opensetc_1}{\gtotalpushc} 
        \arrow[dd, "\iota^*", hook', color=set] \\
        {} 
        \arrow[rrrr, dotted, color=artist] &&&& {} \\
        \cgamma{\opensetc_2}{\dtotalc} 
        \arrow[rrrr, "\vartistc_{\opensetc_2}"', bend right, color=artist] \&  \& 
        \opensetc_2 
        \arrow[ll, "\sheafc_{\dtotalc}"', color=sheaf] 
        \arrow[rr, "\sheafc_{\gtotalpushc}", color=sheaf] 
        \arrow[uu, "\iota" description, hook, color=base] \& \& 
        \cgamma{\opensetc_2}{\gtotalpushc}               
    \end{tikzcd}
    \end{equation}
\end{frame}

\begin{frame}{$\vartist_{\vindexpullc}: \vindexpullc\sheafc_{\dbasec} \rightarrow \sheafc_{\gbasec}$}
    \begin{equation}
  \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf] 
    \arrow[rr, "\sheafc_{\gtotalc}"', color=sheaf] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist] &&&& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf] 
    \arrow[rr, "\sheafc_{\gtotalc}", color=sheaf] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}                                                        
\end{tikzcd}
\end{equation}
\end{frame}

\begin{comment}
